

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add status entries in the order as the appear in the MIB
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\snmpentrys{WR-SWITCH-MIB}{}{wrsGeneralStatusGroup}
    {Group containing collective statuses
    of various subsystems and the main system status, describing the status of
    entire switch.}
    \snmpentrys{WR-SWITCH-MIB}{wrsGeneralStatusGroup}{wrsMainSystemStatus}
	{WRS general status of a switch can
	be \texttt{OK}, \texttt{Warning} or \texttt{Error}. When there is an
	error or warning please check the values of \texttt{wrsOSStatus},
	\texttt{wrsTimingStatus} and \texttt{wrsNetworkingStatus} to find out
	which subsystem causes the problem.}
    \snmpentrys{WR-SWITCH-MIB}{wrsGeneralStatusGroup}{wrsOSStatus}
	{Collective status of the
	\texttt{wrsOSStatusGroup}. For details please check the group's content.}
    \snmpentrys{WR-SWITCH-MIB}{wrsGeneralStatusGroup}{wrsTimingStatus}{
	Collective status of the
	\texttt{wrsTimingStatusGroup}. For details please check the group's
	content.}
    \snmpentrys{WR-SWITCH-MIB}{wrsGeneralStatusGroup}{wrsNetworkingStatus}{
	Collective status of the
	\texttt{wrsNetworkingStatusGroup}. For details please check the group's
	content.}

\snmpentrys{WR-SWITCH-MIB}{}{wrsDetailedStatusesGroup}{
      Branch with collective statuses of various switch subsystems.}

    \snmpentrys{WR-SWITCH-MIB}{wrsDetailedStatusesGroup}{wrsOSStatusGroup}{
	Group with collective statuses of the embedded operating system running on the switch}
	\snmpentrys{WR-SWITCH-MIB}{wrsOSStatusGroup}{wrsBootSuccessful}{
	    Grouped status of
	    \texttt{wrsBootStatusGroup}, indicating whether boot was successful.
	    \texttt{Error} when dot-config source is wrong, unable to get the dot-config,
	    unable to get URL to the dot-config,
	    dot-config contains errors, unable to read the hwinfo, unable to load
	    the FPGA bitstream, unable to load the LM32 software, any kernel
	    modules or userspace daemons are missing.}
	\snmpentrys{WR-SWITCH-MIB}{wrsOSStatusGroup}{wrsTemperatureWarning}{
	    Report whether the temperature
	    thresholds are not set or are exceeded.}
	\snmpentrys{WR-SWITCH-MIB}{wrsOSStatusGroup}{wrsMemoryFreeLow}{
	    \texttt{Warning} when 50\% of the memory is
	    used, error when more than 80\% of the memory is used.}
	\snmpentrys{WR-SWITCH-MIB}{wrsOSStatusGroup}{wrsCpuLoadHigh}{
	    \texttt{Warning} when the average CPU load is
	    more than 2 for the past 1min, 1.5 for 5min or 1 for 15min.
	    \texttt{Error} when the average CPU load is more than 3 for the past
	    1min, 2 for 5min or 1.5 for 15min.}
	\snmpentrys{WR-SWITCH-MIB}{wrsOSStatusGroup}{wrsDiskSpaceLow}{
	    \texttt{Warning} when more than 80\% of any
	    disk partition is used. \texttt{Error} when more than 90\% of any disk
	    partition is used.}

    \snmpentrys{WR-SWITCH-MIB}{wrsDetailedStatusesGroup}{wrsTimingStatusGroup}{
	Group with collective statuses of the timing subsystem.}
	\snmpentrys{WR-SWITCH-MIB}{wrsTimingStatusGroup}{wrsPTPStatus}{
	    \texttt{Error} when any of PTP error counters in
	    \texttt{wrsPtpDataTable} (\texttt{wrsPtpServoStateErrCnt},
	    \texttt{wrsPtpClockOffsetErrCnt} or\\ \texttt{wrsPtpRTTErrCnt}) has
	    increased since the last scan (issue
	    \ref{fail:timing:ppsi_track_phase}, \ref{fail:timing:offset_jump},
	    \ref{fail:timing:rtt_jump}), at least one of the $\Delta_{TXM}$,
	    $\Delta_{RXM}$, $\Delta_{TXS}$, $\Delta_{RXS}$ is 0 (issue
	    \ref{fail:timing:deltas_report}) or PTP servo update counter is not
	    increasing.}
	\snmpentrys{WR-SWITCH-MIB}{wrsTimingStatusGroup}{wrsSoftPLLStatus}{
	    \texttt{Error} when \texttt{wrsSpllSeqState}
	    is not \emph{Ready}, or \texttt{wrsSpllAlignState} is not
	    \emph{Locked} (for Grand Master mode), or any of
	    \texttt{wrsSpllHlock}, \texttt{wrsSpllMlock} equals to 0 (for Slave
	    mode) (issue \ref{fail:timing:spll_unlock}).\\
	    \texttt{Warning} when \texttt{wrsSpllDelCnt} $>$ 0 (for Grand Master
	    mode) or \texttt{wrsSpllDelCnt} has changed (for all other modes).}
	\snmpentrys{WR-SWITCH-MIB}{wrsTimingStatusGroup}{wrsSlaveLinksStatus}{
	    \texttt{Error} when link to Master
	    is down for a switch in the Slave mode (issue
	    \ref{fail:timing:master_down}). Additionally, \texttt{Error} when the
	    link to Master is up for a switch in the Free-running Master or Grand
	    Master mode.}
	\snmpentrys{WR-SWITCH-MIB}{wrsTimingStatusGroup}{wrsPTPFramesFlowing}{
	    \texttt{Error} when PTP Tx/Rx
	    frame counters on active links (Master / Slave ports) are not being
	    incremented. Report the first run.}
	      
    \snmpentrys{WR-SWITCH-MIB}{wrsDetailedStatusesGroup}{wrsNetworkingStatusGroup}{
	  Group with collective statuses of the networking subsystem.}
	\snmpentrys{WR-SWITCH-MIB}{wrsNetworkingStatusGroup}{wrsSFPsStatus}{
	    \texttt{Error} when any of the SFPs
	    reports an error. To find out which SFP caused the problem check
	    \texttt{wrsPortStatusSfpError.<n>}.}
        \snmpentrys{WR-SWITCH-MIB}{wrsNetworkingStatusGroup}{wrsEndpointStatus}{
	    \texttt{Error} when there is a fault
	    in the Endpoint's transmission/reception path (issue
	    \ref{fail:data:ep_txrx}).}
        \snmpentrys{WR-SWITCH-MIB}{wrsNetworkingStatusGroup}{wrsSwcoreStatus}{
	    Not used in the current release.
	    Always reports \texttt{OK}.}
        \snmpentrys{WR-SWITCH-MIB}{wrsNetworkingStatusGroup}{wrsRTUStatus}{
	    \texttt{Error} when RTU is full and cannot
	    accept more requests (issue \ref{fail:data:rtu_full}).}
    \snmpentrys{WR-SWITCH-MIB}{wrsDetailedStatusesGroup}{wrsVersionGroup}{
	    Hardware, gateware and software versions.
	    Additionally the serial number and other hardware information for the WRS.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionSwVersion}{
	    software version (as returned from the \texttt{git describe} at build time).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionSwBuildBy}{
	    software build-by (as returned from the
	    \texttt{git config --get-all user.name} at build time).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionSwBuildDate}{
	    software build date (\texttt{\_\_DATE\_\_} at build time).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionBackplaneVersion}{
	    hardware version of the minibackplane PCB.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionFpgaType}{
	    FPGA model inside the switch.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionManufacturer}{
	    name of the manufacturing company.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionSwitchSerialNumber}{
	    serial number (or string) of the switch.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionScbVersion}{
	    version of the SCB (the motherboard).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionGwVersion}{
	    version of the gateware (FPGA bitstream).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionGwBuild}{
	    build ID of the gateware (FPGA bitstream).}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionSwitchHdlCommitId}{
	    gateware version: commit ID from the \texttt{wr\_switch\_hdl} repository.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionGeneralCoresCommitId}{
	    gateware version: commit ID from the \texttt{general-cores} repository.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionWrCoresCommitId}{
	    gateware version: commit ID from the \texttt{wr-cores} repository.}
	\snmpentrys{WR-SWITCH-MIB}{wrsVersionGroup}{wrsVersionLastUpdateDate}{
	    date and time of last firmware
	    update, this information may not be accurate, due to hard restarts or
	    lack of the proper time at update.}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add expert entries in the order as the appear in the MIB
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\snmpentrye{WR-SWITCH-MIB}{}{wrsOperationStatus}{}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsCurrentTimeGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsCurrentTimeGroup}{wrsDateTAI}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsCurrentTimeGroup}{wrsDateTAIString}{}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsBootStatusGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootCnt}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsRebootCnt}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsRestartReason}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsFaultIP}{Not implemented}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsFaultLR}{Not implemented}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsConfigSource}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsConfigSourceUrl}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsRestartReasonMonit}{
	    Process that caused \texttt{monit} to trigger a restart.}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootConfigStatus}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootHwinfoReadout}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootLoadFPGA}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootLoadLM32}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootKernelModulesMissing}{
	    List of kernel modules is defined in the source code.}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsBootUserspaceDaemonsMissing}{
	    List of daemons is defined in the source code.}
	\snmpentrye{WR-SWITCH-MIB}{wrsBootStatusGroup}{wrsGwWatchdogTimeouts}{
	    Number of times the watchdog has restarted the HDL module responsible for the Ethernet switching process}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsTemperatureGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempFPGA}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempPLL}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempPSL}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempPSR}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempThresholdFPGA}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempThresholdPLL}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempThresholdPSL}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsTemperatureGroup}{wrsTempThresholdPSR}{}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsMemoryGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsMemoryGroup}{wrsMemoryTotal}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsMemoryGroup}{wrsMemoryUsed}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsMemoryGroup}{wrsMemoryUsedPerc}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsMemoryGroup}{wrsMemoryFree}{}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsCpuLoadGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsCpuLoadGroup}{wrsCPULoadAvg1min}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsCpuLoadGroup}{wrsCPULoadAvg5min}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsCpuLoadGroup}{wrsCPULoadAvg15min}{}

    \snmpentrye{WR-SWITCH-MIB}{wrsOperationStatus}{wrsDiskTable}{
	Table with a row for every partition.}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskIndex.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskMountPath.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskSize.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskUsed.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskFree.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskUseRate.<n>}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsDiskTable}{wrsDiskFilesystem.<n>}{}


\snmpentrye{WR-SWITCH-MIB}{}{wrsStartCntGroup}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntHAL}{issue \ref{fail:timing:hal_crash}, \ref{fail:other:daemon_crash}}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntPTP}{issue \ref{fail:timing:ppsi_crash}, \ref{fail:other:daemon_crash}}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntRTUd}{issue \ref{fail:data:rtu_crash}, \ref{fail:other:daemon_crash}}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntSshd}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntHttpd}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntSnmpd}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntSyslogd}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntWrsWatchdog}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsStartCntGroup}{wrsStartCntSPLL}{Not implemented}

\snmpentrye{WR-SWITCH-MIB}{}{wrsSpllState}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsSpllState}{wrsSpllVersionGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllVersionGroup}{wrsSpllVersion}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllVersionGroup}{wrsSpllBuildDate}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsSpllState}{wrsSpllStatusGroup}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllMode}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllIrqCnt}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllSeqState}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllAlignState}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllHlock}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllMlock}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllHY}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllMY}{}
	\snmpentrye{WR-SWITCH-MIB}{wrsSpllStatusGroup}{wrsSpllDelCnt}{}
%		xxx wrsSpllHoldover
%		xxx wrsSpllHoldoverTime
%		xxx (...)
%     \snmpentrye{WR-SWITCH-MIB}{wrsSpllPerPortTable[18]
%	
%		xxx wrsSpllBlock
%		xxx wrsSpllErr
%	

\snmpentrye{WR-SWITCH-MIB}{}{wrsPstatsTable}{Table with pstats values, one row per port.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsIndex.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsPortName.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsTXUnderrun.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXOverrun.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXInvalidCode.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXSyncLost.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPauseFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPfilterDropped.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPCSErrors.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXGiantFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXRuntFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXCRCErrors.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass0.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass1.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass2.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass3.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass4.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass5.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass6.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPclass7.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsTXFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXDropRTUFull.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio0.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio1.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio2.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio3.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio4.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio5.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio6.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRXPrio7.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRTUValid.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRTUResponses.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsRTUDropped.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsFastMatchPriority.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsFastMatchFastForward.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsFastMatchNonForward.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsFastMatchRespValid.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsFullMatchRespValid.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsForwarded.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPstatsTable}{wrsPstatsTRURespValid.<n>}{}

\snmpentrye{WR-SWITCH-MIB}{}{wrsPtpDataTable}{Table with a row per PTP servo instance.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpIndex.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpPortName.<n>}{
	The port on which the instance is running.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpGrandmasterID.<n>}{
	Not implemented.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpOwnID.<n>}{
	Not implemented.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpMode.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpServoState.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpServoStateN.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpPhaseTracking.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpSyncSource.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpClockOffsetPs.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpClockOffsetPsHR.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpSkew.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpRTT.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpLinkLength.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpServoUpdates.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpDeltaTxM.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpDeltaRxM.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpDeltaTxS.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpDeltaRxS.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpServoStateErrCnt.<n>}{
	Number of the servo updates when servo is out of the TRACK\_PHASE.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpClockOffsetErrCnt.<n>}{
	Number of servo updates when
	offset is larger than 500ps or smaller than -500ps.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPtpDataTable}{wrsPtpRTTErrCnt.<n>}{
	Number of servo updates when RTT delta
	between subsequent updates is larger than 1000ps or smaller than -1000ps.}

\snmpentrye{WR-SWITCH-MIB}{}{wrsPortStatusTable}{Table with a row per port.}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusIndex.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusPortName.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusLink.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusConfiguredMode.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusLocked.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusPeer.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpVN.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpPN.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpVS.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpInDB.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpGbE.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusSfpError.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusPtpTxFrames.<n>}{}
    \snmpentrye{WR-SWITCH-MIB}{wrsPortStatusTable}{wrsPortStatusPtpRxFrames.<n>}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add entries from other MIBs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\snmpentryo{HOST-RESOURCES-MIB}{}{hrSWRunName.<n>}{}
\snmpentryo{HOST-RESOURCES-MIB}{}{hrStorageDescr.<n>}{}
\snmpentryo{HOST-RESOURCES-MIB}{}{hrStorageSize.<n>}{}
\snmpentryo{HOST-RESOURCES-MIB}{}{hrStorageUsed.<n>}{}
\snmpentryo{IF-MIB}{}{ifOperStatus.<n>}{}

